Variational Inference for Inverse Reinforcement Learning with Gaussian Processes

### 2019-03-25 mpaper/paper.tex
New data + reorganising files

\begin{figure*}
  \centering
  \begin{minipage}{.5\textwidth}
    \centering
    \includegraphics[width=0.8\columnwidth]{convergence1}
  \end{minipage}%
  \begin{minipage}{.5\textwidth}
    \centering
    \includegraphics[width=0.8\columnwidth]{convergence2}
  \end{minipage}
  \caption{The convergence of $\mathcal{L}$ (at the top) and several example
    policies (at the bottom) over a number of iterations for Scenario~1 on the
    left and Scenario~2 on the right.}
  \label{fig:convergence1}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{parameter_convergence1}
  \includegraphics[width=\textwidth]{parameter_convergence2}
  \caption{Convergence of all optimised parameters for Scenario~1 at the top and
  Scenario~2 at the bottom. In order to represent different variables on the
  same scale, some variables have been $\log$-transformed. Colours denote which
  vector or matrix each scalar comes from: black for $\bm\lambda$,
  \textcolor{blue}{blue} for $\bm\mu$, \textcolor{red}{red} for diagonal
  elements of $\mathbf{B}$, and \textcolor{green}{green} for its non-diagonal
  elements.}
  \label{fig:convergence2}
\end{figure*}

@@

  % \begin{tikzpicture}[
  %   /pgfplots/colormap/viridis,
  %   ellipse2/.style={
  %     draw,
  %     ellipse,
  %     /utils/exec={
  %       \pgfplotscolormapdefinemappedcolor{#1}},
  %     fill=mapped color},
  %   edge2/.style={
  %     ultra thick,
  %     /utils/exec={
  %       \pgfplotscolormapdefinemappedcolor{#1}},
  %     draw=mapped color}]
  %   \csvreader[
  %   no head,
  %   column count=11
  %   ]{covariance_and_policy_transformed.csv}{1=\x, 2=\y, 3=\Soneone, 4=\Stwotwo, 5=\Sthreethree, 6=\Stwoone, 7=\Sthreeone, 8=\Sthreetwo, 9=\ponetwo, 10=\ptwoone, 11=\pthreetwo}{%
  %     \node[ellipse2=\Soneone] (s1) at (3*\x, 2*\y) {$s_1$};
  %     \node[ellipse2=\Stwotwo] (s2) at (3*\x+1, 2*\y+1) {$s_2$};
  %     \node[ellipse2=\Sthreethree] (s3) at (3*\x+2, 2*\y) {$s_3$};
  %     \draw[edge2=\Stwoone] (s1) -- (s2);
  %     \draw[edge2=\Sthreeone] (s1) to (s3);
  %     \draw[edge2=\Sthreetwo] (s2) to (s3);
  %   }
  %   \draw [<->] (2.5, 7.5) node (yaxis) [above] {$\zeta_2$}
  %   |- (11.5, 1.5) node (xaxis) [right] {$\zeta_1$};
  %   \foreach \x in {1, 2, 3} {
  %     \node (x\x) at (1+3*\x, 1.3) {$\x$};
  %   }
  %   \foreach \y in {1, 2, 3} {
  %     \node (y\y) at (2.3, 0.5+2*\y) {$\y$};
  %   }
  % \end{tikzpicture}

\begin{figure}
  \centering
  \begin{tikzpicture}
    \csvreader[
    no head,
    column count=11
    ]{covariance_and_policy_transformed.csv}{1=\x, 2=\y, 3=\Soneone, 4=\Stwotwo, 5=\Sthreethree, 6=\Stwoone, 7=\Sthreeone, 8=\Sthreetwo, 9=\ponetwo, 10=\ptwoone, 11=\pthreetwo}{%
      \begin{axis}[
        ybar=0,
        symbolic x coords={a,b,c},
        ticks=none,
        ymax=1,
        ymin=0,
        x=20,
        bar width=20,
        enlarge x limits=0.25,
        at={(350*\x, 110*\y)},
        height=100,
        bar shift=0pt,
        legend style={
          legend columns=-1,
          at={(1.7,-0.4)}
        }
        ]
        \addplot coordinates {(a, \ponetwo)};
        \addplot coordinates {(b, \ptwoone)};
        \addplot coordinates {(c, \pthreetwo)};
        \draw[dashed] (-50,50) -- (270,50);
        \ifthenelse{\x=2 \AND \y=1}{
          \legend{$\pione$,$\pitwo$,$\pithree$};
        }{}
      \end{axis}
    }
    \draw [<->] (2.3, 8.5) node (yaxis) [above] {$\zeta_2$}
    |- (10, 2) node (xaxis) [right] {$\zeta_1$};
    \foreach \x in {1, 2, 3} {
      \node (x\x) at (1+2.5*\x, 1.7) {$\x$};
    }
    \foreach \y in {1, 2, 3} {
      \node (y\y) at (2.1, 1+2.1*\y) {$\y$};
    }
  \end{tikzpicture}
  \caption{How policy probabilities change after adding more demonstrations. The
    $x$-axis ($y$-axis) shows how many copies of $\zeta_1$ ($\zeta_2$) were in
    $\mathcal{D}$. Each plot shows the values of three policies after 300
    iterations (averaged out over 10 runs). The bottom (top) of each bar plot
    corresponds to probability 0 (1), and dashed lines mark probability 0.5.}
  \label{fig:policies}
\end{figure}

>>>>

\begin{figure*}
  \centering
  \begin{minipage}{.5\textwidth}
    \centering
    \includegraphics[width=0.8\columnwidth]{figures/convergence1}
  \end{minipage}%
  \begin{minipage}{.5\textwidth}
    \centering
    \includegraphics[width=0.8\columnwidth]{figures/convergence2}
  \end{minipage}
  \caption{The convergence of $\mathcal{L}$ (at the top) and several example
    policies (at the bottom) over a number of iterations for Scenario~1 on the
    left and Scenario~2 on the right.}
  \label{fig:convergence1}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{figures/parameter_convergence1}
  \caption{Convergence of all optimised parameters for Scenario~1 at the top and
  Scenario~2 at the bottom. In order to represent different variables on the
  same scale, some variables have been $\log$-transformed. Colours denote which
  vector or matrix each scalar comes from: black for $\bm\lambda$,
  \textcolor{blue}{blue} for $\bm\mu$, \textcolor{red}{red} for diagonal
  elements of $\mathbf{B}$, and \textcolor{green}{green} for its non-diagonal
  elements.}
  \label{fig:convergence2}
\end{figure*}

@@

\begin{figure}
  \centering
  \begin{tikzpicture}[
    /pgfplots/colormap/violet,
    ellipse2/.style={
      draw,
      ellipse,
      /utils/exec={
        \pgfplotscolormapdefinemappedcolor{#1}},
      fill=mapped color},
    edge2/.style={
      ultra thick,
      /utils/exec={
        \pgfplotscolormapdefinemappedcolor{#1}},
      draw=mapped color}]
    \csvreader[
    no head,
    column count=11
    ]{data/median_covariance_transformed.csv}{1=\x, 2=\y, 3=\Soneone, 4=\Stwotwo, 5=\Sthreethree, 6=\Stwoone, 7=\Sthreeone, 8=\Sthreetwo}{%
      \node[ellipse2=\Soneone] (s1) at (3*\x, 2*\y) {$s_1$};
      \node[ellipse2=\Stwotwo] (s2) at (3*\x+1, 2*\y+1) {$s_2$};
      \node[ellipse2=\Sthreethree] (s3) at (3*\x+2, 2*\y) {$s_3$};
      \draw[edge2=\Stwoone] (s1) -- (s2);
      \draw[edge2=\Sthreeone] (s1) to (s3);
      \draw[edge2=\Sthreetwo] (s2) to (s3);
    }
    \draw [<->] (2.5, 7.5) node (yaxis) [above] {$\zeta_2$}
    |- (11.5, 1.5) node (xaxis) [right] {$\zeta_1$};
    \foreach \x in {1, 2, 3} {
      \node (x\x) at (1+3*\x, 1.3) {$\x$};
    }
    \foreach \y in {1, 2, 3} {
      \node (y\y) at (2.3, 0.5+2*\y) {$\y$};
    }
  \end{tikzpicture}
  \end{figure}

\begin{figure}
  \centering
  \begin{tikzpicture}
    \csvreader[
    no head,
    column count=11
    ]{data/covariance_and_policy_transformed.csv}{1=\x, 2=\y, 3=\Soneone, 4=\Stwotwo, 5=\Sthreethree, 6=\Stwoone, 7=\Sthreeone, 8=\Sthreetwo, 9=\ponetwo, 10=\ptwoone, 11=\pthreetwo}{%
      \begin{axis}[
        ybar=0,
        symbolic x coords={a,b,c},
        ticks=none,
        ymax=1,
        ymin=0,
        x=20,
        bar width=20,
        enlarge x limits=0.25,
        at={(350*\x, 110*\y)},
        height=100,
        bar shift=0pt,
        legend style={
          legend columns=-1,
          at={(1.7,-0.4)}
        }
        ]
        \addplot coordinates {(a, \ponetwo)};
        \addplot coordinates {(b, \ptwoone)};
        \addplot coordinates {(c, \pthreetwo)};
        \draw[dashed] (-50,50) -- (270,50);
        \ifthenelse{\x=2 \AND \y=1}{
          \legend{$\pione$,$\pitwo$,$\pithree$};
        }{}
      \end{axis}
    }
    \draw [<->] (2.3, 8.5) node (yaxis) [above] {$\zeta_2$}
    |- (10, 2) node (xaxis) [right] {$\zeta_1$};
    \foreach \x in {1, 2, 3} {
      \node (x\x) at (1+2.5*\x, 1.7) {$\x$};
    }
    \foreach \y in {1, 2, 3} {
      \node (y\y) at (2.1, 1+2.1*\y) {$\y$};
    }
  \end{tikzpicture}
  \caption{How policy probabilities change after adding more demonstrations. The
    $x$-axis ($y$-axis) shows how many copies of $\zeta_1$ ($\zeta_2$) were in
    $\mathcal{D}$. Each plot shows the values of three policies after 300
    iterations (averaged out over 10 runs). The bottom (top) of each bar plot
    corresponds to probability 0 (1), and dashed lines mark probability 0.5.}
  \label{fig:policies}
\end{figure}
